References for PloS paper

### 2014-01-08 image_analysis_paper/plos_draft.tex
Added some to writeup

@@

@@

\begin{table}
	\begin{tabular}{| p{0.3\textwidth} | c | c | p{0.3\textwidth} |}
		\hline 
		Method & Spearman's $\rho$ & Execution Time & Notes About Method \\ 
		\hline 
		PCA on one-dimensional profiles & 0.9244 & $< 1$ second & \\
		\hline 
		DMAPS on one-dimensional profiles & 0.9209 & $< 1$ second & \\
		\hline 
		Angular synchronization + DMAPS on one-dimensional profiles & 0.9164 & $< 1$ second & \\
		\hline 
		VDM on one-dimensional profiles & 0.9232 & $< 1$ second & \\	
		\hline 
		VDM on two-dimensional images & 0.9051  & $325$ seconds & $\mathcal{O}(n^2)$ to compute the pairwise alignments\\
		\hline 	
		Scattering transform + DMAPS on two-dimensional profiles & 0.9011  & $86$ seconds &  $\mathcal{O}(n)$ to compute the scattering transform for each data point \\
		\hline
	\end{tabular}
\end{table}
% You may title this section "Methods" or "Models".
% "Models" is not a valid title for PLoS ONE authors. However, PLoS ONE
% authors may use "Analysis"
\section*{Materials and Methods}

@@

>>>>

The issue of rotation invariance arises in many applications, most commonly image registration and image alignment.
%
In settings such as face recognition, medical imaging, and computer vision, objects from different frames or timepoints must be aligned or ``registered'' before further analysis can be done.
%
For example, often medical images (such as MRI scans) are collected over multiple days, and doctors would like to study development of a condition (such as the growth of a tumor).
%
However, on each day, the patient and/or sensors may be in slightly different locations; therefore, the images must be aligned before the doctor can look at how the tumor is growing and evolving.

Several different techniques have been developed to solve the image registration problem. 
%
Most of these techniques are ``template-based'' techniques, where one selects a prototypical image or ``template'', and then aligns the remaining images to this template \cite{...}.
%
Such techniques can suffer if a good template is not know {\em a priori}; when the images are noisy, selecting one image from the data set at random can yield a noisy template and result in many mis-alignments.

In addition, most existing techniques rely on feature extraction algorithms, and these features are often problem-specific.
%
For example, (ADD INFO ABOUT FACES).

We are interested in analyzing data collected from developing {\em Drosophila} embryos during nuclear cycle 14 (NC14) (CHECK).
%
(ADD MORE ABOUT WHY THIS IS IMPORTANT).

Currently, data is collected using a high-throughput microfluidic device \cite{chung2010microfluidic}; we can therefore image hundreds of embryos in one experiment.
%
Each embryo is stained for the membrane proteins, dpERK, and DI. 
%
We image the cross-section of each embryo.
%
We then use image analysis software to extract the circular dpERK concentration profile from the fluorescent image.
%
We use the expression of DI to find the dorsal midline of the embryo, and ``unzip'' the circular profile at the dorsal midline to obtain a one-dimensional, linear dpERK concentration profile.
%
We then measure the membrane thickness of them embryo; the thickness of the membrane is known to be monotonic in time during NC14 \cite{...}. 
%
We then order the concentration profiles for each embryo by the thickness of the membrane to obtain a ``reconstruction'' of the dynamics of dpERK.

@@

Here,  we will discuss alternative methodologies to reconstruct the dpERK dynamics from fluorescent images. 
%
We will use various data mining techniques to {\em automatically} order the dpERK concentration profiles in time.
%
We will not only focus on the linear concentration profiles extracted from the images, but also work directly with the two-dimensional dpERK fluorescent images. 
%
Finally, we will look at ordering the two-dimensional membrane images in time; these are much more feature-rich than the dpERK images, and prove to be more challenging.

@@

\begin{table}
	\begin{tabular}{| p{0.3\textwidth} | c | c | p{0.3\textwidth} |}
		\hline 
		Method & Spearman's $\rho$ & Execution Time & Notes About Method \\ 
		\hline 
		PCA on one-dimensional profiles & 0.9244 & $< 1$ second & \\
		\hline 
		DMAPS on one-dimensional profiles & 0.9209 & $< 1$ second & \\
		\hline 
		Angular synchronization + DMAPS on one-dimensional profiles & 0.9164 & $< 1$ second & \\
		\hline 
		VDM on one-dimensional profiles & 0.9232 & $< 1$ second & \\	
		\hline 
		VDM on two-dimensional images & 0.9051  & $325$ seconds & $\mathcal{O}(n^2)$ to compute the pairwise alignments\\
		\hline 	
		Scattering transform + DMAPS on two-dimensional profiles & 0.9011  & $86$ seconds &  $\mathcal{O}(n)$ to compute the scattering transform for each data point \\
		\hline
		Scattering transform + DMAPS on two-dimensional membrane images & 0.8403  & $300$ seconds &  $\mathcal{O}(n)$ to compute the scattering transform for each data point \\
		\hline
	\end{tabular}
\end{table}
% You may title this section "Methods" or "Models".
% "Models" is not a valid title for PLoS ONE authors. However, PLoS ONE
% authors may use "Analysis"
\section*{Materials and Methods}

@@

\subsection*{Edge detection}
For the membrane images, we are only interested in the location of the edges of the membrane (not other features, such as the intensity of the fluorescent stain).
%
We therefore preprocess the
